% !TEX spellcheck = en_US
% GeneratorSpeed
%=================================================================================
In addition to the challenge described in the previous section \ref{RatedWindSpeed} another one was discovered during the first iteration of the steady states calculation. The rated conditions where met before the control region 2.5 is reached. The cause of this was the rated generator speed of $\Omega_{\text{G,rated}} = \SI{458}{rpm}$ was set too high with the aerodynamic efficiency at this time. After discovering this issue and addressing it with the electrical drive train team, a new design value was provided (see Steady States \ref{steady states}). This was done by increasing the number off poles in the generator.

The issue was not fully resolved because an infinite design loop was triggered. Hence the mechanical drive train team was not calculating the gearbox ratio $r_{\text{GB}}$ with the $\lambda_{\text{opt}} = 8.75$ but with another design value proposed by the management: The tip speed at $\lambda_{\text{opt}}$. 
Which is defined as $v_{\text{Tip}} = \SI{80}{m/s}$. 

So after the changes of the generator speed $\Omega_{\text{G,rated}}$ a new gearbox ratio $r_{\text{GB}}$ was calculated this would lead to the same issue described in the paragraph above. After clarification with the management the issue was resolved because the used tip speed was only a maximal value $v_{\text{Tip}} = \hat{v}_{\text{Tip}}$. The tip speed was not fixed. The resulting solution is to keep the original gearbox ratio and adjust the generator speed as described above.      